Demes: a specification for interchanging complex demography

### 2021-06-18 paper.tex
Update section on reproducibilty.

@@

A standard format also serves to improve scientific reproducibility. Authors simply include their demographic model as a supplementary file, or upload it to a data repository, so that readers need not transcribe the model themselves. This removes the opportunity for error due to model misinterpretation or incorrect translation to a simulatable format. In the event that the Demes standard becomes outdated, published Demes files will be convertible to future formats with relative ease because the data model is unambiguously specified.

>>>>

    \item Why we've versioned the specification, and how we've planned
    for future extensions.

@@

Reproducibility is a significant problem throughout the
sciences~\citep{baker20161} and various measures have been
proposed to increase the likelihood of researchers being
able to replicate results in the
literature~\citep{munafo2017manifesto}. The most basic requirement
for reproducibility is that we must be able to state precisely what
the result in question is. The lack of standardisation in how
complex demographic models are communicated today, and the lack of
precision in the published model descriptions means that it is difficult
to replicate analyses, or reproduce those models for later simulation.
Thus, we hope that the Demes standard introduced here will be widely adopted
by inference methods and the results reported in publications
routinely included as supplemental material or uploaded to a data
repository in Demes format.

\jkcomment{sketch of last paragraph}
Another basic requirement for scientific progress in the inference
of demographic models is that we should be able to compare the output
of one method to the output of another, or to compare an inferred
demography to some simulated ground truth. Demes facilitates this,
paving the way for things like methods competitions. PopSim
Consortium FTW!
